A Search for Circumstellar Companions of Sirius B

### 2021-07-30 paper/paper.tex
update paper

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities at sub-AU separations, down to an ultimate sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}. Despite the high sensitivity of our observations, we do not detect any companions around Sirius B. These observations showcase that for nearby faint targets direct imaging is limited more by background noise than absolute contrast.
\end{abstract}

@@

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Being able to probe the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. The process required to image a planet is daunting, however. The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim10^{-8}$, and for a Sun-Earth system are $\sim10^{-10}$ \citep{traub_direct_2010}. In addition, the close angular separation of planets makes it difficult to distinguish them from the diffraction pattern of the star and other noise sources. In order to make such a difficult detection it is imperative to minimize diffraction, scattering, and systematic noise.

Nearby white dwarfs (within $\sim$\qty{100}{\parsec}) are compelling targets for direct imaging searches, despite the limited knowledge of planetary systems around evolved stars. \cite{burleigh_imaging_2002} suggests planets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\solarmass}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf. Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, however the tidal forces on planets that readily escape engulfment are negligible. During the asymptotic giant (AGB) phase, strong ionizing soft X-ray and UV emission will likely photoevaporate planetary atmospheres. In addition, the mass loss of the star will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.

If the planet has managed to survive through the RGB and AGB phases, stars below \qty{8}{\solarmass} will enter the white dwarf cooling sequence, which will lead to a reduction in luminosity by $10^3-10^4$. This means the contrast between a white dwarf and a companion will be 3-4 orders of magnitude lower than the equivalent main sequence system. The combination of expanded orbits and lower contrast are beneficial for imaging, due to the limited inner working angles and sensitivities of ground-based instrumentation. The transit photometry method is very insensitive to planets around white dwarfs because the probability of a transit decreases with increasing separation. Similarly, the radial velocity method is limited to very massive planets on larger separations in addition to the extremely broad spectral features of a white dwarf which greatly limit the precision of radial velocity measurements.

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by looking for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. This excess could likely be attributed to circumstellar dust or gas discs, which are indicators of the planetary formation history. Of the $\sim$ 100 white dwarfs they studied, no companions were found. The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38. Eventually this excess was determined to be from a dust disc \citep{telesco_observations_1990}, with the current interpretation associating the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.

The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a very wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}. Sirius B has also been imaged, which will be discussed later. To date, there has been no direct images of an exoplanet around a white dwarf.

The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, an A1Vm star known for being the brightest in the night sky, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,collaboration_gaia_2018}. The proximity and brightness of the Sirius system make it one of the most well-studied systems throughout history \citep[see][]{wesemael_sirius_1982}.

The orbit of Sirius B was first studied by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. \citet{bond_companion_1862} reported and confirmed visual evidence of Sirius B by Alvan G. Clark and his father. \citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be very similar to a main-sequence early A-type star despite the faintness, which we know know to be typical of white dwarf spectra.

Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864}, with the first orbital solution including dynamic masses published by \citet{van_den_bos_orbit_1960}. \citet{gatewood_study_1978} improved upon the van den Bos orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary. \citet{bond_sirius_2017} greatly refine the orbit using a compilation of historical data and HST data, which gives dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.

The precise dynamical masses are key for finding the age of Sirius; \citet{bond_sirius_2017} report a cooling age for Sirius B of \qty{126}{\mega\year} using isochrones. Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\solarmass}, which when combined with stellar evolution codes yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}. The precision of the system age is useful for constraining the mass of potential companions.

@@

Some of the first modern studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}). \citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\jupitermass} at \ang{;;3} (\qty{7.9}{\au}). \citet{skemer_sirius_2011} used mid-IR (out to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Very recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast is split depending on which half of the FOV is being considered. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

@@

We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the extremely bright (-1.35 K-band magnitude) diffraction patterns would sweep into the field of view (FOV) of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light. This is very similar to the issues reported by \citet[\S2]{vigan_high-contrast_2015} in their attempts to image Sirius B. In order to overcome these issues, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

@@

During each observation, calibration frames were taken in the form of dark frames and sky flat frames. We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF. The co-registered frames are then shifted to the center of the FOV. Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch. With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}. We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}. For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}). All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles have been made available on Zenodo \citep{lucas_nirc2_2021}.

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{psf}
    \caption{The median frame from the 2020-11-21 epoch showing the instrumental PSF. The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}. The speckle pattern can be seen in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
    \label{fig:psf}
\end{figure}

@@

We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve. The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics. The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above. We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}. The collapsed residual frames along with the above metrics for each algorithm for each epoch can be found in \autoref{sec:adi-results}.

@@

All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}. All of the code for the ADI processing in this paper, including the scripts for each figure produced can be found at the GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} in Jupyter notebooks and Julia scripts.

@@

\begin{figure*}
    \centering
    \epsscale{0.95}
    \plotone{stim}
    \caption{The STIM maps for each epoch calculated from the residual cube. Note that the STIM probability has a typical cutoff threshold of 0.5 for significant detections. The inner full-width at half-maximum (FWHM) is masked out for each map.}
    \label{fig:stim}
\end{figure*}

@@

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms have been shown to outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen. Due to the nature of high-contrast imaging, it is extremely difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no evidence for IR excess from a circumstellar disk. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.

The contrast maps from the best performing algorithm for each reduction are shown in \autoref{fig:contrast}. We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}). Then we use an age of \qty{226}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}. It is important to note how the precision of the system age (see \autoref{sec:intro}) leads to quite accurate interpolation on the evolutionary grids. The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the sky-background limited regime.

@@

In this work we demonstrate the results of high-contrast images of Sirius B in the near-IR. Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au}. In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}. Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.

@@

In recent years improving contrast and inner working angle were the dominant parameters of interest. Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the background noise than the speckle noise. Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}. This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.

In closing,

@@

\begin{figure}[h!]
    \centering
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components. Each frame was been cropped to the inner \ang{;;0.25}. The inner FWHM has been masked out in each frame. The width of the circles represent the uncertainty.}
\end{figure}

>>>>

\begin{abstract}
We present deep imaging of Sirius B, the closest and brightest white dwarf. We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging. We reach sub-Jupiter sensitivities at sub-AU separations, down to an ultimate sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}. Despite the high sensitivity of our observations, we do not detect any companions around Sirius B, which is consistent with previous studies. These observations showcase that for nearby faint targets direct imaging is ultimately limited by background noise more than contrast.
\end{abstract}

@@

High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets. Being able to probe the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory. The process required to image a planet is daunting, however. The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{-8}$, and for a Sun-Earth system are $\sim$$10^{-10}$ \citep{traub_direct_2010}. In addition, the close angular separation of planets makes it difficult to detect them over the diffraction pattern of the star and other noise sources. In order to make such a difficult detection it is imperative to minimize diffraction, scattering, and systematic noise.

Typical targets for imaging are nearby young stars; the close proximity decreases the projected separation of the inner working angle (IWA) of the instrument, allowing closer investigation, and younger exoplanets are hotter and therefore the contrast is reduced. Another way to reduce contrast would be to reduce the luminosity of the star, which is not possible during the main-sequence (MS) lifetime of a star but is possible in the latest stages of stellar evolution. When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) reach the end of their lifetimes, they become white dwarfs and begin cooling, which reduces their luminosity by a factor of $10^3-10^4$ compared to their progenitors. The faintness, broad spectral lines, and  expanded orbits, as we will discuss below, all make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods. However, the faintness reduces the contrast of planetary companions and the expanded separation greatly benefit imaging.

White dwarfs do present challenges, and there is limited knowledge of planetary systems around evolved stars. \cite{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the red giant (RGB) phase. Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible. During the asymptotic giant (AGB) phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}. Overall, the probability of discovering a \textit{first-generation} planet around a white dwarf is low, but there are potential methods for \textit{second-generation} planets to exist after the violent RGB and AGB phases.

The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by looking for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry. This excess could likely be attributed to circumstellar dust or gas discs, which are indicators of the planetary formation history. Of the $\sim$100 white dwarfs they studied, no companions were found. The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38. Eventually this excess was determined to be from a dust disc \citep{telesco_observations_1990}, with the current interpretation associating the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.

To date, there has been no direct images of an exoplanet around a white dwarf. The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}. The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}. The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.

A particularly fascinating white dwarf is Sirius B, the closest and brightest white dwarf. The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}. As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging, and additionally it is a young system ($\sim$\qty{225}{\mega\year}), further reducing the predicted contrast necessary to image a planetary companion.

The orbit of Sirius B was first studied by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''. This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B. \citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.

Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864}, with the first orbital solution including dynamic masses published by \citet{van_den_bos_orbit_1960}. \citet{gatewood_study_1978} improved upon the \citeauthor{van_den_bos_orbit_1960} orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary. \citet{bond_sirius_2017} greatly refined the orbit using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.

The precise dynamical masses are key for finding the age of Sirius; \citet{bond_sirius_2017} report a cooling age for Sirius B of \qty{126}{\mega\year} using isochrones. Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}. The precision of the system age is useful for constraining the mass of potential companions.

@@

Some of the first modern imaging studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}). \citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\jupitermass} at \ang{;;3} (\qty{7.9}{\au}). \citet{skemer_sirius_2011} used mid-IR (out to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B. \citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}. Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B. Because of the simultaneous observation, their contrast depended on which region of the FOV was tested. Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.

@@

We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}). Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A. The adaptive optics (AO) calibration failed when the -1.35 K-band magnitude diffraction patterns from Sirius A would sweep into the field of view (FOV) of the wavefront sensor (WFS). Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light. \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B. In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.

@@

During each observation, we took calibration frames in the form of dark frames and sky flat frames. We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.

@@

For each epoch we applied a flat correction using calibration frames captured during observing. We also removed bad pixels using a combination of L.A.Cosmic \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm. We removed sky background using a high-pass median filter with a box size of 31 pixels. For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter. At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}. Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF. The co-registered frames are then shifted to the center of the FOV. Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch. With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}. We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}. For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}). All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo \citep{lucas_nirc2_2021}.

\begin{figure}
    \centering
    \epsscale{1.1}
    \plotone{psf}
    \caption{The median frame from the 2020-11-21 epoch showing the instrumental PSF. The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}. The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
    \label{fig:psf}
\end{figure}

@@

We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve. The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics. The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above. We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}. The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \autoref{sec:adi-results}.

@@

All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}. All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} in Jupyter notebooks and Julia scripts.

@@

\begin{figure*}
    \centering
    \epsscale{0.95}
    \plotone{stim}
    \caption{The STIM maps for each epoch calculated from the residual cube. The STIM probability has a typical cutoff threshold of 0.5 for significant detections. The inner full-width at half-maximum (FWHM) is masked out for each map.}
    \label{fig:stim}
\end{figure*}

@@

It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF. Both of these algorithms outperform traditional median and PCA subtraction for disk imaging. In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen. Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess. Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.

The contrast maps from the best performing algorithm for each reduction are shown in \autoref{fig:contrast}. We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}). Then we use an age of \qty{226}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}. It is important to note how the precision of the system age (see \autoref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids. The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the sky-background limited regime.

@@

In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR. While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets. In this work we present high-contrast images of Sirius B in the near-IR. Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au}. In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}. Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.

In recent years improving contrast and inner working angle were the dominant parameters of interest. Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the sky background than the speckle noise. Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}. This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.

@@

@@

\begin{figure}[h!]
    \centering
    \plotone{orbit_frames}
    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components. Each frame was cropped to the inner \ang{;;0.25} and the inner FWHM has been masked out. The width of the circles represent the uncertainty.}
\end{figure}
